A template for the \emph{arxiv} style

### 2022-12-14 paper-rmd/trial_level_mlm_noise_based.tex
updated rmd and avg code

\begin{tikzpicture}
      % Define nodes
      \node[obs]                               (y) {$y_{ijk}$};
      \node[det, above=2.5cm of y] (mu) {$\mu_{ijk}$};
      \node[det, above=2.5cm of mu, xshift=-1.2cm]  (d) {$d_j$};
      \node[det, above=2.5cm of mu, xshift=1.2cm]  (d_prime) {$d_j'$};
      \node[latent, above=of d]  (delta) {$\delta_j$};
      \node[latent, above=of d_prime]  (delta_delta) {$\Delta\delta_j$};
      \node[latent, left=1cm of mu]            (p) {$\vec{\theta}_{jk}$};
      \node[latent, above=1cm of y]  (theta) {$\vec{p}_{ijk}$};
      \node[latent, left=1cm of theta]  (kappa) {$\kappa_j$};
      \node[latent, above=of delta, xshift=-.5cm]  (delta_pop) {$\overline{\delta}$};
      \node[latent, above=of delta_delta, xshift=-.5cm]  (delta_delta_pop) {$\overline{\Delta\delta}$};
      \node[latent, above=of delta, xshift=.5cm]  (sigma_delta) {$\sigma_{\delta}$};
      \node[latent, above=of delta_delta, xshift=.5cm]  (sigma_delta_delta) {$\sigma_{\Delta\delta}$};
      \node[latent, right=2cm of theta]  (phi) {$\phi$};
      \node[obs, above= of mu]  (x) {$x_{ijk}$};
      % Connect the nodes
      \edge {theta} {y} ; %
      \edge {d, d_prime} {mu}
      \edge {delta} {d, d_prime}
      \edge {delta_delta} {d_prime}
      \edge {p, x} {mu}
      \edge {delta_pop} {delta}
      \edge {delta_delta_pop} {delta_delta}
      \edge {sigma_delta} {delta}
      \edge {sigma_delta_delta} {delta_delta}
      \edge {mu, phi, kappa} {theta}

      % Plates
      {
        \tikzset{plate caption/.append style={below=15pt of #1.south east}};
        \tikzstyle{plateIJK} = [align=center];
        \plate[inner sep=0.25cm, xshift=-.0625cm] {plateIJK} {(mu)(y)(theta)(x)} {$i$} ;
     }
      {
        \tikzset{plate caption/.append style={above right=0pt of #1.north east}};
        \plate[inner sep=0.25cm, xshift=-.12cm, yshift=-.12cm] {plateJ} {(mu)(y)(p)(d)(d_prime)(delta)(delta_delta)(kappa)} {$j$} ;
      }
      {
        \tikzset{plate caption/.append style={above right=0pt and 0pt of #1.north west}};
        \plate[inner sep=0.25cm] {plateIJ} {(p)(mu)(y)(x)} {$k$};
      }

@@

  \end{minipage}%
  \begin{minipage}{.5\textwidth}
    \centering
    $
\begin{aligned}[c]
  y_{ijk} &\sim Categorical(\overrightarrow{\theta_{ijk}}) \\
  \overrightarrow{p_{ijk}} &= Z_{NB}(\mu_{ijk},\kappa_j, \phi) \\
  \mu_{ijk} &= f_{NB}(\overrightarrow{\theta_{jk}}, d_j, d'_j, x_{ijk})  \\
  d_j &= \frac{1}{2} \ \text{logistic}(\delta_j) \\
  d_j’ &= \frac{1}{2} \ \text{logistic}\big(\delta_j + \exp(\Delta\delta_j)\big) \\
  \delta_j &\sim Normal(0,1) \\
  \Delta\delta_j &\sim Normal(0,1) \\
  log(\sigma_{\eta}) &\sim Normal(-.5, .5) \\
  log(\sigma_{\Delta\eta}) &\sim Normal(-.5, -.5) \\
  log(\sigma_{\beta}) &\sim Normal(-1, .5) \\
  \overrightarrow{\theta_{jk}} &\sim Dirichlet_4(\overrightarrow{1}) \\
  \overrightarrow{\phi} &\sim Dirichlet_3(\overrightarrow{1}) \\
\end{aligned}
$
  \end{minipage}
  \caption{Hierarchical complex trial-level noise-based model diagram and formula specifications. $Z_{NB}$ and $f_{NB}$ are functions that compute the probability of each categorical response and the expected proportion of read-out mental samples given underlying mental probabilities and sample reading noise. See Appendix for further descriptions of these details.}
\end{figure}

>>>>

\begin{tikzpicture}
      % Define nodes
      \node[obs]                               (y) {$y_{ijk}$};
      \node[det, above=2.5cm of y] (mu) {$\mu_{ijk}$};
      \node[det, above=2.5cm of mu, xshift=-1.2cm]  (d) {$d_j$};
      \node[det, above=2.5cm of mu, xshift=1.2cm]  (d_prime) {$d_j'$};
      \node[latent, above=of d]  (delta) {$\delta_j$};
      \node[latent, above=of d_prime]  (delta_delta) {$\Delta\delta_j$};
      \node[latent, left=1cm of mu]            (p) {$\vec{\theta}_{jk}$};
      \node[latent, above=1cm of y]  (theta) {$\vec{p}_{ijk}$};
      \node[latent, left=1cm of theta]  (N) {$N_j$};
      \node[latent, above=of delta, xshift=-.5cm]  (delta_pop) {$\overline{\delta}$};
      \node[latent, above=of delta_delta, xshift=-.5cm]  (delta_delta_pop) {$\overline{\Delta\delta}$};
      \node[latent, above=of delta, xshift=.5cm]  (sigma_delta) {$\sigma_{\delta}$};
      \node[latent, above=of delta_delta, xshift=.5cm]  (sigma_delta_delta) {$\sigma_{\Delta\delta}$};
      \node[latent, right=2cm of theta]  (phi) {$\phi$};
      \node[obs, above= of mu]  (x) {$x_{ijk}$};
      % Connect the nodes
      \edge {theta} {y} ; %
      \edge {d, d_prime} {mu}
      \edge {delta} {d, d_prime}
      \edge {delta_delta} {d_prime}
      \edge {p, x} {mu}
      \edge {delta_pop} {delta}
      \edge {delta_delta_pop} {delta_delta}
      \edge {sigma_delta} {delta}
      \edge {sigma_delta_delta} {delta_delta}
      \edge {mu, phi, N} {theta}

      % Plates
      {
        \tikzset{plate caption/.append style={below=15pt of #1.south east}};
        \tikzstyle{plateIJK} = [align=center];
        \plate[inner sep=0.25cm, xshift=-.0625cm] {plateIJK} {(mu)(y)(theta)(x)} {$i$} ;
     }
      {
        \tikzset{plate caption/.append style={above right=0pt of #1.north east}};
        \plate[inner sep=0.25cm, xshift=-.12cm, yshift=-.12cm] {plateJ} {(mu)(y)(p)(d)(d_prime)(delta)(delta_delta)(N)} {$j$} ;
      }
      {
        \tikzset{plate caption/.append style={above right=0pt and 0pt of #1.north west}};
        \plate[inner sep=0.25cm] {plateIJ} {(p)(mu)(y)(x)} {$k$};
      }

@@

  \end{minipage}%
  \begin{minipage}{.5\textwidth}
    \centering
    $
\begin{aligned}[c]
  y_{ijk} &\sim Categorical(\overrightarrow{\theta_{ijk}}) \\
  \overrightarrow{p_{ijk}} &= Z_{NB}(\mu_{ijk},N_j, \phi) \\
  \mu_{ijk} &= f_{NB}(\overrightarrow{\theta_{jk}}, d_j, d'_j, x_{ijk})  \\
  d_j &= \frac{1}{2} \ \text{logistic}(\delta_j) \\
  d_j’ &= \frac{1}{2} \ \text{logistic}\big(\delta_j + \exp(\Delta\delta_j)\big) \\
  \delta_j &\sim Normal(0,1) \\
  \Delta\delta_j &\sim Normal(0,1) \\
  log(\sigma_{\eta}) &\sim Normal(-.5, .5) \\
  log(\sigma_{\Delta\eta}) &\sim Normal(-.5, -.5) \\
  log(\sigma_{\beta}) &\sim Normal(-1, .5) \\
  \overrightarrow{\theta_{jk}} &\sim Dirichlet_4(\overrightarrow{1}) \\
  \overrightarrow{\phi} &\sim Dirichlet_3(\overrightarrow{1}) \\
  N_j &\sim Cauchy(20) \\
\end{aligned}
$
  \end{minipage}
  \caption{Hierarchical complex trial-level noise-based model diagram and formula specifications. $Z_{NB}$ and $f_{NB}$ are functions that compute the probability of each categorical response and the expected proportion of read-out mental samples given underlying mental probabilities and sample reading noise. See Appendix for further descriptions of these details.}
\end{figure}
